\bf What is the Best Way to Display Two Time Series to Read Association?

### 2016-01-25 paper/paper.Rnw
fixing lots of small things, captions, figure styles

\begin{figure}[htbp]
  \centering
<<lineup.example, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
set.seed(1234)
a <- gen_true_data(24, 0.95)
td <- gather(a, variable, value, c(X1, X2))
b <- gen_null(24)
nd_l <- gather(b, variable, value, c(X1, X2))
pos <- 7
td <- data.frame(.n=rep(pos, nrow(td)), td)
lg <- nd_l$.n < pos
nd_l1 <- data.frame(.n=nd_l$.n[lg], t=nd_l$t[lg], variable=nd_l$variable[lg], 
                    value=nd_l$value[lg])
nd_l2 <- data.frame(.n=nd_l$.n[!lg], t=nd_l$t[!lg], variable=nd_l$variable[!lg], 
                    value=nd_l$value[!lg])
nd_l2$.n <- nd_l2$.n + 1
d <- rbind(nd_l1, td, nd_l2)

ggplot(data=d, aes(x=t, y=value, colour=variable)) + geom_line() + facet_wrap(~.n, ncol=4, scales="free_y")  +
    theme_bw() + theme(axis.title.x = element_blank(),
                       axis.title.y = element_blank(),
                       axis.text.x = element_blank(),
                       axis.text.y = element_blank(),
                       axis.ticks = element_blank(),
                       legend.position="none")
@
  \caption{A lineup ($m = 20$) of line graphs. Which plot shows the series with the strongest correlation?}
  \label{lineup:example}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<smoothing, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
set.seed(123)
uns <- gen_true_data(96, 0.8)
uns_l <- gather(uns, variable, value, -t)
p1a <- ggplot(data=uns_l, aes(x=t, y=value, colour=variable)) + geom_line() +labs(title="Unsmoothed Overlaid Lines") +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p3a <- ggplot(data=uns, aes(x=X1, y=X2)) + geom_point()+ labs(title="Unsmoothed Scatterplot)") +
    theme(aspect.ratio=1, axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")

set.seed(123)
sm <- gen_true_data(96, 0.8, smoothed = TRUE)
sm_l <- gather(sm, variable, value, -t)
p2a <- ggplot(data=sm_l, aes(x=t, y=value, colour=variable)) + geom_line() + labs(title="Smoothed Overlaid Lines") +
      theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p4a <- ggplot(data=sm, aes(x=X1, y=X2)) + geom_point() + labs(title="Smoothed Scatterplot") +
    theme(aspect.ratio=1, axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")

grid.arrange(p1a, p2a, p3a, p4a, ncol=2)
@
  \caption{The same AR(1) data both unsmoothed and smoothed for both plot designs. t = 96, correlation = 0.86}
  \label{smoothing}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<designs, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
set.seed(101)
a <- gen_true_data(24, 0.95)
b <- gen_true_data(24, -0.95)
a_l <- gather(a, variable, value, -t)
b_l <- gather(b, variable, value, -t)
p1b <- ggplot(data=a_l, aes(x=t, y=value, colour=variable)) + geom_line() + labs(title="Overlaid line graph") +
      theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p2b <- ggplot(data=b_l, aes(x=t, y=value, colour=variable)) + geom_line() + labs(title="Overlaid line graph") +
      theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p3b <- ggplot(data=a, aes(x=X1, y=X2)) + geom_point() + labs(title="Scatterplot") +
      theme(aspect.ratio=1, axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p4b <- ggplot(data=b, aes(x=X1, y=X2)) + geom_point() + labs(title="Scatterplot") +
      theme(aspect.ratio=1, axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
grid.arrange(p1b, p2b, p3b, p4b, ncol=2)
@
  \caption{The same two data sets in both plot designs. t=24, correlation (left) = 0.946, correlation (right) = -0.943}
  \label{designs}
\end{figure}

@@

\begin{figure}[htbp]
 \centering
<<results, dependson='setup', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, error=FALSE, message=FALSE>>=
ggplot(data=bylineup, aes(x=r, y=percent, colour=design)) + geom_smooth(se=F) + geom_point() + facet_grid(n~smoothed) + 
  scale_colour_discrete(name = "Plot Design") + labs(y="True plot detection rate", x="Correlation") +
  theme(legend.position="bottom")
@
  \caption{Response accuracy for unsmoothed data, broken by unsmoothed (left), smoothed (right) and sample size. The dots are data points, the lines represent a naive model average fit. Both plot designs have similar performance for positively correlated data, however the overlaid line graphs are much weaker at revealing negative correlation.}
    \label{results}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<powerdiff, dependson='setup', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
prop <- select(bylineup, smoothed, n, evals, total, r, design)
prop <- summarise(group_by(prop, smoothed, n, r), l.attempt=sum(ifelse(design=="Overlaid Lines", evals, 0)),
                                                  l.detect=sum(ifelse(design=="Overlaid Lines", total, 0)),
                                                  s.attempt=sum(ifelse(design=="Scatterplot", evals, 0)),
                                                  s.detect=sum(ifelse(design=="Scatterplot", total, 0)))
alpha <- 1-(1-0.95^(1/48))/2 
##8 correlations * 6 design = 48 boxplots, so this the students t quantile for the joint 95% CI
prop <- mutate(prop, l.power = l.detect/l.attempt, 
               s.power = s.detect/s.attempt,
               df = s.attempt + l.attempt - 1, 
               difference=s.power-l.power, 
               t = qt(alpha, df),
               se = sqrt(s.power*(1-s.power)/s.attempt+l.power*(1-l.power)/l.attempt),
               upper = difference + t*se,
               lower = difference - t*se)
ggplot(data=prop) + geom_errorbar(aes(x=r, ymax=upper, ymin=lower)) + geom_point(aes(x=r, y=difference)) +
        geom_hline(aes(yint=0, colour="red")) + labs(x="Correlation", y="Scatterplot power minus Overlaid Lines") + facet_grid(n~smoothed)
@
 \caption{The difference in estimated power (scatter plot power minus overlaid line power) to reveal the true plot by smoothness and sample size with a joint 95\% confidence interval. The red line indicates the point where both plot designs are equally powerful The largest differences appear in negative correlation, where the overlaid lines power drops substantially.}
 \label{powerdiff}
\end{figure}

\begin{figure}[htbp]
  \centering
<<samplesize, dependson='setup', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
ggplot(data=subset(bylineup, smoothed==0), aes(x=r, y=percent, colour=factor(n))) + geom_smooth(se=F) + geom_point() + facet_grid(design~.) + scale_colour_discrete(name = "Sample size") +  labs(y="Percent Detected", x="Correlation") + theme(legend.position="bottom")
@
 \caption{Replotting figure~\ref{results} to highlight the effects of changes in sample size of unsmoothed data. The scatter plot appears to universally benefit from increased sample sizes but the overlaid lines only see a benefit in positive correlation.}
 \label{samplesize}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<confidence2, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
conf2 <- select(full, conf_level, r, smoothed, n, design) #c(7, 15
qplot(r, 6-conf_level, data=conf2, alpha=I(0.1)) + 
  geom_smooth(method="loess") + 
  facet_grid(n~design+smoothed) +
  labs(x = "Correlation", y = "Confidence (5=High, 1=Low)")
@
  \caption{Reported confidence against true plot correlation. Darker points indicate a confidence level selected more regularly. Strong correlation is more often associated with a lower reported confidence.}
 \label{confidence2}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<pins, dependson='setup', fig.width=6, fig.height=10, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
count.setup <- select(full, pic_id, response_0, actual_location, design, smoothed, n)
count.setup$response_0 <- as.character(count.setup$response_0)
counts <- data.frame(table(count.setup$pic_id, count.setup$response_0))
counts$Var1 <- as.numeric(as.character(counts$Var1))
counts$Var2 <- as.numeric(as.character(counts$Var2))
colnames(counts) <- c("lineup", "plot", "count")
pin <- merge(counts, bylineup, by.x="lineup", by.y="pic_id")
pin <- select(pin, lineup, plot, count, smoothed, actual_location, n, design, r, evals)
pin <- mutate(pin, r = factor(r),
              true = ifelse(plot==actual_location, "True plot", "Null plot"), 
              percent = count/evals,
              base = 0,
              correlation = diag(as.matrix(correl[pin$lineup, (pin$plot+2)])))
pin.a <- ggplot(data=filter(pin, smoothed==0 & design == "Scatterplot")) + 
         geom_errorbar(aes(x=correlation, ymin=base, ymax=percent, colour=true)) +
         geom_point(aes(x=correlation, y=percent, colour=true)) + coord_fixed() + facet_grid(n~r) + 
         labs(title ="Unsmoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
pin.b <- ggplot(data=subset(pin, smoothed==1 & design == "Scatterplot")) + 
         geom_errorbar(aes(x=correlation, ymin=base, ymax=percent, colour=true)) +
         geom_point(aes(x=correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + 
         labs(title="Smoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
pin.c <- ggplot(data=subset(pin, smoothed==0 & design == "Overlaid Lines")) +
         geom_errorbar(aes(x=correlation, ymin=base, ymax=percent, colour=true)) +
         geom_point(aes(x=correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) +
         labs(title="Unsmoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
pin.d <- ggplot(data=subset(pin, smoothed==1 & design == "Overlaid Lines")) + 
         geom_errorbar(aes(x=correlation, ymin=base, ymax=percent, colour=true)) +
         geom_point(aes(x=correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + 
         labs(title="Smoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
grid.arrange(pin.a, pin.b, pin.c, pin.d, ncol=1)
@
  \caption{Pin plots of the subject selections of each lineup, by design, smoothness, true plot correlaition and sample size. On the x-axis is the correlation of the plot (there typically is spurious correlation in the null plots), and on the y-axis is the proportion of times a plot was chosen. Each plot contains data from the three lineups with the requisite factor combination. Red pins indicate null plots and blue indicates the true plot, occasionally the true plot does not seem to appear as it has a proportion of zero and is visually blocked by the red pins. Strongly correlated plot seem to be selected regardless of if the relationship is real or spurious.}
  \label{pins}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{anom1}
  \caption{A lineup of unsmoothed scatter plots with a sample size of 24. The true plot is located in position 4 with a correlation of -0.491, and was selected by one out of eleven observers (p = 0.33). The plot in position 6 was selected by nine of these eleven observers (p < 0.001) despite having a correlation of -0.037. Subjects most often cited the clustering effect shown as the reason for their selection, an example of the over-interpretation of randomness.}
    \label{anom1}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{anom2}
  \caption{A lineup of unsmoothed overlaid lines with a sample size of 12 and true correlation of -0.707. The true plot in position 8 was not detected in five evaluations. However, the null plot in position 13 was selected four times, (p –value < 0.001) despite having a correlation of only 0.225. When asked for a reason of their selections, subjects typically answered that the lines were close together, another misleading visual artefact of the random data.} 
  \label{anom2}
\end{figure}

@@

\begin{figure}[htbp]
 \centering
<<powermodel, dependson='setup', fig.height=8, fig.width=8, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
predplot <- prediction %>% filter(is.na(detected)) %>%
            select(r, t, rsgn, smoothed, design, subj_id, RandomEf, FixedEf) %>%
            mutate(RandomEf = exp(RandomEf)/(1+exp(RandomEf)), 
                   FixedEf = exp(FixedEf)/(1+exp(FixedEf)))
##Logit link function transform

>>>>

\begin{figure}[htbp]
  \centering
<<lineup.example, dependson='setup', fig.width=6, fig.height=6, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
set.seed(1234)
a <- gen_true_data(24, 0.95)
td <- gather(a, variable, value, c(X1, X2))
b <- gen_null(24)
nd_l <- gather(b, variable, value, c(X1, X2))
pos <- 7
td <- data.frame(.n=rep(pos, nrow(td)), td)
lg <- nd_l$.n < pos
nd_l1 <- data.frame(.n=nd_l$.n[lg], t=nd_l$t[lg], variable=nd_l$variable[lg], 
                    value=nd_l$value[lg])
nd_l2 <- data.frame(.n=nd_l$.n[!lg], t=nd_l$t[!lg], variable=nd_l$variable[!lg], 
                    value=nd_l$value[!lg])
nd_l2$.n <- nd_l2$.n + 1
d <- rbind(nd_l1, td, nd_l2)

ggplot(data=d, aes(x=t, y=value, colour=variable)) + geom_line() + facet_wrap(~.n, ncol=4, scales="free_y")  +
    theme_bw() + theme(axis.title.x = element_blank(),
                       axis.title.y = element_blank(),
                       axis.text.x = element_blank(),
                       axis.text.y = element_blank(),
                       axis.ticks = element_blank(),
                       legend.position="none")
@
  \caption{Lineup of overlaid line graphs of size $m = 20$. In which plot are the two series most strongly associated?}
  \label{lineup:example}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{smootha}
<<smoothing, dependson='setup', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
set.seed(123)
uns <- gen_true_data(96, 0.8)
uns_l <- gather(uns, variable, value, -t)
set.seed(123)
sm <- gen_true_data(96, 0.8, smoothed = TRUE)
sm_l <- gather(sm, variable, value, -t)
ggplot(data=uns_l, aes(x=t, y=value, colour=variable)) + geom_line() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{smoothb}
<<smoothing2, dependson='smoothing', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=uns, aes(x=X1, y=X2)) + geom_point() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{smoothc}
<<smoothing3, dependson='smoothing', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=sm_l, aes(x=t, y=value, colour=variable)) + geom_line() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{smoothd}
<<smoothing4, dependson='smoothing', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=sm, aes(x=X1, y=X2)) + geom_point() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
  \caption{Plots illustrating the experimental design. The same AR(1) data both unsmoothed (\subref{smootha} and \subref{smoothb}) and smoothed (\subref{smoothc} and \subref{smoothd}) for both plot designs, with t = 96 and correlation = 0.86}
  \label{smoothing}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{designa}
<<designs, dependson='setup', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
set.seed(101)
a <- gen_true_data(24, 0.95)
b <- gen_true_data(24, -0.95)
a_l <- gather(a, variable, value, -t)
b_l <- gather(b, variable, value, -t)
ggplot(data=a_l, aes(x=t, y=value, colour=variable)) + geom_line() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{designb}
<<designs2, dependson='designs', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=b_l, aes(x=t, y=value, colour=variable)) + geom_line() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{designc}
<<designs3, dependson='designs', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=a, aes(x=X1, y=X2)) + geom_point() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{designd}
<<designs4, dependson='designs', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=b, aes(x=X1, y=X2)) + geom_point() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\caption{Plots illustrating the experimental design: the two different plot types of the same data with $t=24$, $r= 0.946$ (\subref{designa} and \subref{designc}), $r= -0.943$ (\subref{designb} and \subref{designd}).}
\label{designs}
\end{figure}

@@

\begin{figure}[htbp]
 \centering
<<results, dependson='setup', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, error=FALSE, message=FALSE>>=
ggplot(data=bylineup, aes(x=r, y=percent, colour=design)) + geom_smooth(se=F) + geom_point() + facet_grid(n~smoothed) + 
  scale_colour_discrete(name = "Plot Design") + labs(y="Detection rate", x="Correlation") +
  theme(legend.position="bottom")
@
  \caption{Response accuracy for unsmoothed data, broken by unsmoothed (left), smoothed (right) and sample size. The dots are data points, the lines represent a naive model average fit. Both plot designs have similar performance for positively correlated data, however the overlaid line graphs are much weaker at revealing negative correlation.}
    \label{results}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<powerdiff, dependson='setup', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
prop <- select(bylineup, smoothed, n, evals, total, r, design)
prop <- summarise(group_by(prop, smoothed, n, r), l.attempt=sum(ifelse(design=="Overlaid Lines", evals, 0)),
                                                  l.detect=sum(ifelse(design=="Overlaid Lines", total, 0)),
                                                  s.attempt=sum(ifelse(design=="Scatterplot", evals, 0)),
                                                  s.detect=sum(ifelse(design=="Scatterplot", total, 0)))
alpha <- 1-(1-0.95^(1/48))/2 
##8 correlations * 6 design = 48 boxplots, so this the students t quantile for the joint 95% CI
prop <- mutate(prop, l.power = l.detect/l.attempt, 
               s.power = s.detect/s.attempt,
               df = s.attempt + l.attempt - 1, 
               difference=s.power-l.power, 
               t = qt(alpha, df),
               se = sqrt(s.power*(1-s.power)/s.attempt+l.power*(1-l.power)/l.attempt),
               upper = difference + t*se,
               lower = difference - t*se)
ggplot(data=prop) + geom_errorbar(aes(x=r, ymax=upper, ymin=lower)) + geom_point(aes(x=r, y=difference)) +
        geom_hline(aes(yintercept=0, colour="red")) + labs(x="Correlation", y="Power difference") + facet_grid(n~smoothed)
@
 \caption{The difference in estimated power (scatter plot power minus overlaid line power) to reveal the true plot by smoothness and sample size with a joint 95\% confidence interval. The red line indicates the point where both plot designs are equally powerful The largest differences appear in negative correlation, where the overlaid lines power drops substantially.}
 \label{powerdiff}
\end{figure}

\begin{figure}[htbp]
  \centering
<<samplesize, dependson='setup', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
ggplot(data=subset(bylineup, smoothed==0), aes(x=r, y=percent, colour=factor(n))) + geom_smooth(se=F) + geom_point() + facet_grid(design~.) + scale_colour_discrete(name = "Sample size") +  labs(y="Detection rate", x="Correlation") + theme(legend.position="bottom")
@
 \caption{Replotting figure~\ref{results} to highlight the effects of changes in sample size of unsmoothed data. The scatter plot appears to universally benefit from increased sample sizes but the overlaid lines only see a benefit in positive correlation.}
 \label{samplesize}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<confidence2, dependson='setup', fig.width=6, fig.height=6, out.width='0.9\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
conf2 <- select(full, conf_level, r, smoothed, n, design) #c(7, 15
qplot(r, 6-conf_level, data=conf2, alpha=I(0.1)) + 
  geom_smooth(method="loess") + 
  facet_grid(n~design+smoothed) +
  labs(x = "Correlation", y = "Confidence (5=High, 1=Low)")
@
  \caption{Reported confidence against true plot correlation. Darker points indicate a confidence level selected more regularly. Strong correlation is more often associated with a lower reported confidence.}
 \label{confidence2}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
%  \begin{subfigure}[htbp]{1\textwidth}
%\subcaption{}\label{pin1}
<<pins, dependson='setup', fig.height=4, fig.width=7, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
count.setup <- select(full, pic_id, response_0, actual_location, design, smoothed, n)
count.setup$response_0 <- as.character(count.setup$response_0)
counts <- data.frame(table(count.setup$pic_id, count.setup$response_0))
counts$Var1 <- as.numeric(as.character(counts$Var1))
counts$Var2 <- as.numeric(as.character(counts$Var2))
colnames(counts) <- c("lineup", "plot", "count")
pin <- merge(counts, bylineup, by.x="lineup", by.y="pic_id")
pin <- select(pin, lineup, plot, count, smoothed, actual_location, n, design, r, evals)
pin <- mutate(pin, r = factor(r),
              true = ifelse(plot==actual_location, "True plot", "Null plot"), 
              percent = count/evals,
              base = 0,
              correlation = diag(as.matrix(correl[pin$lineup, (pin$plot+2)])))
pin$design <- factor(pin$design, levels=c("Scatterplot", "Overlaid Lines"), labels=c("scat","lines"))
pin$smoothed <- factor(pin$smoothed, levels=c("0", "1"), labels=c("N","Y"))
#ggplot(data=filter(pin, smoothed==0 & design == "Scatterplot")) + 
#         geom_errorbar(aes(x=correlation, ymin=base, ymax=percent, colour=true)) +
#         geom_point(aes(x=correlation, y=percent, colour=true))  + facet_grid(n~r) +
#         scale_x_continuous(breaks=c(-1,0,1)) + scale_y_continuous(breaks=c(0,0.5,1)) +
#         labs(y="Proportion",x="") + theme(legend.position="none")
@
%\end{subfigure}
%\begin{subfigure}[htbp]{1\textwidth}
%\subcaption{Scatterplots}\label{pin2}
<<pin2, dependson='pins', fig.height=8, fig.width=7, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=subset(pin)) + 
         geom_errorbar(aes(x=correlation, ymin=base, ymax=percent, colour=true)) +
         geom_point(aes(x=correlation, y=percent, colour=true)) + facet_grid(design+n+smoothed~r) + 
         scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels=c("1","-","0","+","1")) + 
         scale_y_continuous(breaks=c(0,0.5,1)) +
         labs(y="Proportion",x="Correlation between series") + theme(legend.position="none")
#ggplot(data=subset(pin, design == "Scatterplot")) + 
#         geom_errorbar(aes(x=correlation, ymin=base, ymax=percent, colour=true)) +
#         geom_point(aes(x=correlation, y=percent, colour=true)) + facet_grid(n+smoothed~r) + 
#         scale_x_continuous(breaks=c(-1,0,1)) + scale_y_continuous(breaks=c(0,0.5,1)) +
#         labs(y="Proportion",x="Correlation") + theme(legend.position="none")
#ggplot(data=subset(pin, smoothed==1 & design == "Scatterplot")) + 
#         geom_errorbar(aes(x=correlation, ymin=base, ymax=percent, colour=true)) +
#         geom_point(aes(x=correlation, y=percent, colour=true)) + facet_grid(n~r) + 
#         scale_x_continuous(breaks=c(-1,0,1)) + scale_y_continuous(breaks=c(0,0.5,1)) +
#         labs(y="Proportion",x="") + theme(legend.position="none")
@
%\end{subfigure}
%\begin{subfigure}[htbp]{1\textwidth}
%\subcaption{}\label{pin3}
<<pin3, dependson='pin', fig.height=5, fig.width=7, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
#ggplot(data=subset(pin, smoothed==0 & design == "Overlaid Lines")) +
#         geom_errorbar(aes(x=correlation, ymin=base, ymax=percent, colour=true)) +
#         geom_point(aes(x=correlation, y=percent, colour=true)) + facet_grid(n~r) +         
#         scale_x_continuous(breaks=c(-1,0,1)) + scale_y_continuous(breaks=c(0,0.5,1)) +
#         labs(y="Proportion",x="") + theme(legend.position="none")
@
%\end{subfigure}
%\begin{subfigure}[htbp]{1\textwidth}
%\subcaption{Overlaid line graphs}\label{pin4}
<<pin4, dependson='smoothing', fig.height=5, fig.width=7, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
#ggplot(data=subset(pin, design == "Overlaid Lines")) + 
#         geom_errorbar(aes(x=correlation, ymin=base, ymax=percent, colour=true)) +
#         geom_point(aes(x=correlation, y=percent, colour=true)) + facet_grid(n+smoothed~r) + 
#         scale_x_continuous(breaks=c(-1,0,1)) + scale_y_continuous(breaks=c(0,0.5,1))+
#         labs(y="Proportion",x="Correlation") + theme(legend.position="none")
@
%\end{subfigure}
  \caption{Pin plots showing subject selections for each plot in all lineups for all factor levels in the experiment. Proportion of times plot selected plotted by correlation between series in each plot. Blue indicates data plot. Longer pins indicate more people selected that plot in the lineup. Results for the three replicate lineups for each treatment are  plotted together. Generally, subjects selected the plot from the lineup with the strongest association. With small sample size this is less obvious. For overlaid lines, subjects tended to more often pick the plot showing the strongest positive association, particularly if the correlation between series in the data plot was low. }   
    %: (\subref{pin1}) unsmoothed scatterplots, (\subref{pin2}) smoothed scatterplots, (\subref{pin3}) unsmoothed overlaid lines, (\subref{pin4}) smoothed overlaid lines. On the x-axis is the correlation of the plot (there typically is spurious correlation in the null plots), and on the y-axis is the proportion of times a plot was chosen. Each plot contains data from the three lineups with the requisite factor combination. Red pins indicate null plots and blue indicates the true plot, occasionally the true plot does not seem to appear as it has a proportion of zero and is visually blocked by the red pins. Strongly correlated plot seem to be selected regardless of if the relationship is real or spurious.}
  \label{pins}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.9\textwidth]{anom1}
  \caption{A lineup of unsmoothed scatter plots with a sample size of 24. The true plot is located in position 4 with a correlation of -0.491, and was selected by one out of eleven observers (p = 0.33). The plot in position 6 was selected by nine of these eleven observers (p < 0.001) despite having a correlation of -0.037. Subjects most often cited the clustering effect shown as the reason for their selection, an example of the over-interpretation of randomness.}
    \label{anom1}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.9\textwidth]{anom2}
  \caption{A lineup of unsmoothed overlaid lines with a sample size of 12 and true correlation of -0.707. The true plot in position 8 was not detected in five evaluations. However, the null plot in position 13 was selected four times, (p –value < 0.001) despite having a correlation of only 0.225. When asked for a reason of their selections, subjects typically answered that the lines were close together, another misleading visual artefact of the random data.} 
  \label{anom2}
\end{figure}

@@

\begin{figure}[htbp]
 \centering
<<powermodel, dependson='setup', fig.height=8, fig.width=8, out.width='0.9\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
predplot <- prediction %>% filter(is.na(detected)) %>%
            select(r, t, rsgn, smoothed, design, subj_id, RandomEf, FixedEf) %>%
            mutate(RandomEf = exp(RandomEf)/(1+exp(RandomEf)), 
                   FixedEf = exp(FixedEf)/(1+exp(FixedEf)))
##Logit link function transform
